\documentclass[line, margin, 12pt]{res}

\usepackage{hyperref}
\usepackage{amsmath,scalerel}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}

\newcommand\aspace[1][5cm]{\hspace*{#1}} % To add horizontal space of 5cm
\DeclareMathOperator*{\Bigcdot}{\scalerel*{\cdot}{\bigodot}}


\begin{document}

\name{\aspace \huge\bf{\href{https://darshan.sh}{Darshan Sharma}}}
\address{\hspace{2mm}
~\textbullet~\href{mailto:thedarshansharma@gmail.com}{thedarshansharma@gmail.com} 
~\textbullet~+91-7009746321  ~\textbullet~ Chandigarh, 160047~\textbullet~{\href{https://darshan.sh}{darshan.sh}}~\aspace}

\begin{resume}

\section{EXPERIENCE}
\begin{itemize}
\item \textbf{Total EXPERIENCE = 4 years}\\
\item \textbf{Frontend Developer at ConsultIT \hspace{10mm} June 2020-Aug 2022}\\
\textbf {TechStack: Flutter, ReactJs, NodeJs, MongoDB, Redis, GraphQL}\\
Developed a web panel for interviewers in ReactJs.\\
Developed a aptitude based mobile application in Flutter.\\
Worked mainly on the payment handling(IN-APP purchases), video creation and storage part of the mobile app developement.\\
Published 2 apps on Google Play Store.
\item \textbf{Freelance Web Devloper \hspace{20mm} May 2019 - May 2020}\\
\textbf{TechStack: ReactJs, AWS, NodeJs}\\
Developed websites in ReactJS and NestJs for client (mainly frontend part).\\
Worked on functional components of ReactJS and helped one of the client in transitioning from class based component to functional components in ReactJs. \\ 
Helped one of the client on failed deployments on aws (aws appconfig, aws cdk toolkit). \\
Helped one of the client where issue was dirty reads in database. 
\item \textbf{Software Engineer at Block8 \hspace{20mm} May 2018-May 2019}\\
\textbf{TechStack: ReactJS, NodeJS, MongoDB}\\
Created a web application where transfer of shares happen.Also integrated stripe for payments part.
\end{itemize}

\section{\hyperref[https://www.github.com/darshansharma]{PROJECTS}}
\begin{itemize}
\item \textbf{{MyStake}}\\
Website to buy and or sell shares at the same time.  Used blockchain technology to store the transactions.\\
 \textbf{Tech - ReactJS, NodeJs,  MongoDB, Webpack}
\item \textbf{\href{https://play.google.com/store/apps/details?id=com.darshansharma.simple_reels_downloader}{Simple Reels Downloader}}\\
Mobile application made in Flutter to download Instagram reels video. It is live on Android Play Store.\\
 \textbf{Tech - Flutter}
\item \textbf{\href{https://darshan.sh}{darshan.sh }}\\
A blogging website which I use to write blogs (monthly). And also my portfolio website. \\
 \textbf{Tech - Flutter, Firestore, Cloud Functions}
\end{itemize}

\section{EDUCATION}
\begin{itemize}
\item B.E in Computer Science and Engineering \\
 Panjab University \\
CGPA: 8.11 / 10.0 \\
\item \textbf{High School -} Kendriya Vidyalaya (CBSE) - 9.2 CGPA
\item \textbf{Secondary School -} Kendriya Vidyalaya (CBSE) - 84.2\%
\item \textbf{GATE Rank -} 1248\\
\end{itemize}

\section{TECHNICAL SKILLS}
\begin{itemize}
\item \textbf{Frontend:} HTML, CSS ReactJs, Flutter, MongDB,PostgreSQL,AWS,docker
\item \textbf{Backend:}  Python, NodeJs, NestJs, ExpressJs
\item \textbf{Tools:} webpack
\end{itemize}

\end{resume}
\end{document}
